Water discharge has a variable impact on sediment transport capacity in subglacial systems

### 2023-08-25 Delaneyetal2023b.tex
Updates from Overleaf

Over time scales longer than days to weeks, the glacier's sediment transport capacity reacts to the ice thickness, controlling the channel closure rate, and the surface slope of the glacier, in addition to water discharge \citep[Figure~\ref{fig:multi_run}, ~ Section~\ref{sect:sub_mode}; ][]{rothlisberger1972,shreve1972,stevens2022}.
If the glacier is in a supply-limited state, often assumed in landscape evolution models, then the sediment discharge record also represents additional processes of sediment availability and bedrock erosion from  water pressure variations and sliding  \citep[e.g.][]{iverson2012,herman2015,delaney2023}.
This multitude of processes lies in contrast to most subaerial systems, where transport capacity typically increases with water discharge and hydraulic gradient, and the hydraulic gradient generally remains stable over time scales ranging from years to millennia \citep[Section~\ref{sect:fluv}; e.g.][]{muller1968,whipple1999,wickert2019}.
The stronger link between sediment export and hydrological forcing in subaerial channels means that variations in sediment transport records can be more easily attributed to climatic conditions than in  subglacial systems

>>>>

Over time scales longer than days to weeks, the glacier's sediment transport capacity reacts to the ice thickness, controlling the channel closure rate, and the surface slope of the glacier, in addition to water discharge \citep[Figure~\ref{fig:multi_run}, ~ Section~\ref{sect:sub_mode}; ][]{rothlisberger1972,shreve1972,stevens2022}.
If the glacier is in a supply-limited state, often assumed in landscape evolution models, then the sediment discharge record also represents additional processes of sediment availability and bedrock erosion from  water pressure variations and sliding  \citep[e.g.][]{iverson2012,herman2015,delaney2023}.
This multitude of processes lies in contrast to most subaerial systems, where transport capacity typically increases with water discharge and hydraulic gradient, and the hydraulic gradient generally remains stable over time scales ranging from years to millennia \citep[Section~\ref{sect:fluv}; e.g.][]{muller1968,whipple1999,wickert2019}.
The stronger link between sediment transport capacity and hydrological forcing in subaerial channels means that variations in sediment transport records can be more easily attributed to climatic conditions than in  subglacial systems.
